---
title: "miRNA_survival"
author: "Patrick Lac"
date: "April 25, 2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r library}
library(tidyverse)
library(dplyr)
library(RobustRankAggreg)
library(mirbase.db)
```

Let's load in our data:

``` {r data}
miRNA_AMLPMP <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table3_significant_miRNAs_by_Cox_in_PMP.csv")
miRNA_TCGA <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table1_significant_miRNAs_by_Cox_in_TCGA.csv")
```

```{r rename column}
colnames(miRNA_AMLPMP)[1] <- "miRNA"
colnames(miRNA_TCGA)[1] <- "miRNA"
```

``` {r order_miRNAs}
AMLPMP_ordered_miRS <- miRNA_AMLPMP[order(miRNA_AMLPMP$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

TCGA_ordered_miRs <- miRNA_TCGA[order(miRNA_TCGA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now let's filter for shared miRNAs only:
``` {r filter_shared_miRNAs}
AMLPMP_shared_miRNA <- filter(miRNA_AMLPMP, miRNA_AMLPMP$miRNA %in% miRNA_TCGA$miRNA)
TCGA_shared_miRNA <- filter(miRNA_TCGA, miRNA_TCGA$miRNA %in% miRNA_AMLPMP$miRNA)
```

Next, we will order the shared miRNAs by significance
``` {r order_miRNAs}
AMLPMP_ordered_shared_miRs <- AMLPMP_shared_miRNA[order(AMLPMP_shared_miRNA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

TCGA_ordered_shared_miRs <- TCGA_shared_miRNA[order(TCGA_shared_miRNA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now, we will aggregate the ordered miRNAs 
``` {r aggregate_miRNAs}
glist <- c(AMLPMP_ordered_shared_miRs, TCGA_ordered_shared_miRs)

miRNA_agg <- aggregateRanks(glist = glist, method = "RRA", exact = T)
miRNA_agg
```
The p-values are all at 1 - why? because this method relies on comparing relative positions between miRNAs within the data (eg. whether a>b in both datasets). The positions of the miRNAs are highly inconsistent relative to one another between these datasets so the package is unable to come up with a p-value


### Now let's look at the Xp11.23 miRNAs only
``` {r Xp11.23.data}
xp11.23_AMLPMP <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table4_significant_Xp11.23_miRNAs_by_Cox_in_PMP.csv")
xp11.23_TCGA <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table2_significant_Xp11.23_miRNAs_by_Cox_in_TCGA.csv")
```

```{r rename column}
colnames(xp11.23_AMLPMP)[1] <- "miRNA"
colnames(xp11.23_TCGA)[1] <- "miRNA"
```

Now let's filter for shared miRNAs only:
``` {r filter_shared_xp11.23}
AMLPMP_shared_xp11.23 <- filter(xp11.23_AMLPMP, xp11.23_AMLPMP$miRNA %in% xp11.23_TCGA$miRNA)
TCGA_shared_xp11.23 <- filter(xp11.23_TCGA, xp11.23_TCGA$miRNA %in% xp11.23_AMLPMP$miRNA)
```

Next, we will order the shared miRNAs by significance
``` {r order_xp11.23}
AMLPMP_shared_xp11.23_ordered <- AMLPMP_shared_xp11.23[order(AMLPMP_shared_xp11.23$p_value_ward_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

TCGA_shared_xp11.23_ordered <- TCGA_shared_xp11.23[order(TCGA_shared_xp11.23$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now, we will aggregate the ordered xp11.23 miRNAs using RobustRankAggreg
``` {r aggregate_xp11.23}
glist.xp11.23 <- c(AMLPMP_shared_xp11.23_ordered, TCGA_shared_xp11.23_ordered)

xp11.23_agg <- aggregateRanks(glist = glist.xp11.23, method = "RRA")
xp11.23_agg
```

Now let's get the chromosome locations and cluster information for the miRs in the shared list
```{r shared_miRs_location}
miRNAs <- as.character(miRNA_agg[,1])

x <- mirbaseCLUSTER
clL <- eapply(x, length)
id <- names(clL[clL > 1])[1]
get(miRNAs, x)
```
```{r shared_miRs_location}
miRNAs <- as.character(xp11.23_agg[,1])

x <- mirbaseCLUSTER
clL <- eapply(x, length)
id <- names(clL[clL > 1])[1]
get(miRNAs, x)
```
``` {r chromosome}
x <- mirbaseCLUSTER
# Get the first cluster containg more than one element
clL <- eapply(x, length)
id <- names(clL[clL > 1])
get(id, x)

```
