---
title: "miRNA_survival"
author: "Patrick Lac"
date: "April 25, 2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r library}
library(tidyverse)
library(dplyr)
library(RobustRankAggreg)
library(RankAggreg)
```

Let's load in our data:

``` {r data}
miRNA_AMLPMP <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table3_significant_miRNAs_by_Cox_in_PMP.csv")
miRNA_TCGA <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table1_significant_miRNAs_by_Cox_in_TCGA.csv")
```

``` {r order_miRNAs}
AMLPMP_ordered_miRS <- miRNA_AMLPMP[order(miRNA_AMLPMP$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

TCGA_ordered_miRs <- miRNA_TCGA[order(miRNA_TCGA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now let's filter for shared miRNAs only:
``` {r filter_shared_miRNAs}
AMLPMP_shared_miRNA <- filter(miRNA_AMLPMP, miRNA_AMLPMP$ï..miRNA %in% miRNA_TCGA$ï..miRNA)
TCGA_shared_miRNA <- filter(miRNA_TCGA, miRNA_TCGA$ï..miRNA %in% miRNA_AMLPMP$ï..miRNA)
```

Next, we will order the shared miRNAs by significance
``` {r order_miRNAs}
AMLPMP_ordered_shared_miRs <- AMLPMP_shared_miRNA[order(AMLPMP_shared_miRNA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

TCGA_ordered_shared_miRs <- TCGA_shared_miRNA[order(TCGA_shared_miRNA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now, we will aggregate the ordered miRNAs 
``` {r aggregate_miRNAs}
glist <- c(AMLPMP_ordered_miRS, TCGA_ordered_miRs)

miRNA_agg <- aggregateRanks(glist = glist, method = "RRA", exact = T)
miRNA_agg
```
The p-values are all at 1 - why? because this method relies on comparing relative positions between miRNAs within the data (eg. whether a>b in both datasets). The positions of the miRNAs are highly inconsistent relative to one another between these datasets so the package is unable to come up with a p-value

## Trying RankAggreg package
This package simulates 

``` {r RankAggreg matrices}
miR532ranks.total <- matrix(c(AMLPMP_ordered_miRS[1:170],
              TCGA_ordered_miRs[1:170]), byrow=TRUE, ncol=170)

miR532ranks.shared <- matrix(c(AMLPMP_ordered_shared_miRs,
              TCGA_ordered_shared_miRs), byrow=TRUE, ncol=52)
```

First let's aggregate using Spearman's. This looks at the "distance" of miRNAs and does not consider how miRNAs relate to one another
``` {r Aggregate.all.miRs.Spearman}
(CES <- RankAggreg(miR532ranks.total, 25, weights=NULL, method="CE", distance="Spearman", rho=.1, convIn=30))
plot(CES)
```

``` {r Aggregate.all.miRs.Kendall}
(CES <- RankAggreg(miR532ranks.total, 25, weights=NULL, method="CE", distance="Kendall", rho=.1, convIn=7))
plot(CES)
```

``` {r Aggregate.shared.miRs.Spearman}
(CES <- RankAggreg(miR532ranks.shared, 25, weights=NULL, method="CE", distance="Spearman", rho=.1, convIn=30))
plot(CES)
```

``` {r Aggregate.all.miRs.Kendall}
(CES <- RankAggreg(miR532ranks.shared, 25, weights=NULL, method="CE", distance="Kendall", rho=.1, convIn=7))
plot(CES)
```

### Now let's look at the Xp11.23 miRNAs only
``` {r Xp11.23.data}
xp11.23_AMLPMP <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table4_significant_Xp11.23_miRNAs_by_Cox_in_PMP.csv")
xp11.23_TCGA <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table2_significant_Xp11.23_miRNAs_by_Cox_in_TCGA.csv")
```

Now let's filter for shared miRNAs only:
``` {r filter_shared_xp11.23}
AMLPMP_shared_xp11.23 <- filter(xp11.23_AMLPMP, xp11.23_AMLPMP$ï..miRNA %in% xp11.23_TCGA$ï..miRNA)
TCGA_shared_xp11.23 <- filter(xp11.23_TCGA, xp11.23_TCGA$ï..miRNA %in% xp11.23_AMLPMP$ï..miRNA)
```

Next, we will order the shared miRNAs by significance
``` {r order_xp11.23}
AMLPMP_shared_xp11.23_ordered <- AMLPMP_shared_xp11.23[order(AMLPMP_shared_xp11.23$p_value_ward_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

TCGA_shared_xp11.23_ordered <- TCGA_shared_xp11.23[order(TCGA_shared_xp11.23$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now, we will aggregate the ordered xp11.23 miRNAs using RobustRankAggreg
``` {r aggregate_xp11.23}
glist.xp11.23 <- c(AMLPMP_shared_xp11.23_ordered, TCGA_shared_xp11.23_ordered)

xp11.23_agg <- aggregateRanks(glist = glist.xp11.23, method = "RRA")
xp11.23_agg
```

It has the same issue as with the entire list.  The relative positions of the miRNAs are not consistent between the two datasets.

In that case, let's aggregate using RanKAggreg's Spearman method
``` {r Aggregate.shared.miRs.Spearman}
xp11.23.shared.matrix <- matrix(c(AMLPMP_shared_xp11.23_ordered,
              TCGA_shared_xp11.23_ordered), byrow=TRUE, ncol=13)

(CES.xp11.23 <- RankAggreg(xp11.23.shared.matrix, 13, weights=NULL, method="CE", distance="Spearman", rho=.1, convIn=30))
plot(CES.xp11.23)
```
