---
title: "miRNA_primaryAML_survival"
author: "Patrick Lac"
date: "May 2, 2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r library}
library(tidyverse)
library(dplyr)
library(RobustRankAggreg)
library(RankAggreg)
```

Let's load in our data:

``` {r data}
miRNA_AMLPMP_Primary <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table7_significant_miRNAs_by_Cox_in_primary_PMP.csv")
miRNA_TCGA_Primary <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Xp11.23/Data/Table1_significant_miRNAs_by_Cox_in_TCGA.csv")
```

```{r rename column}
colnames(miRNA_AMLPMP_Primary)[1] <- "miRNA"
colnames(miRNA_TCGA_Primary)[1] <- "miRNA"
```

Now let's filter for shared miRNAs only:
``` {r filter_shared_miRNAs}
Primary_AMLPMP_shared_miRNA <- filter(miRNA_AMLPMP_Primary, miRNA_AMLPMP_Primary$miRNA %in% miRNA_TCGA_Primary$miRNA)
Primary_TCGA_shared_miRNA <- filter(miRNA_TCGA_Primary, miRNA_TCGA_Primary$miRNA %in% miRNA_AMLPMP_Primary$miRNA)
```

Next, we will order the shared miRNAs by significance
``` {r order_miRNAs}
Primary_AMLPMP_ordered_shared_miRs <- Primary_AMLPMP_shared_miRNA[order(Primary_AMLPMP_shared_miRNA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)

Primary_TCGA_ordered_shared_miRs <- Primary_TCGA_shared_miRNA[order(Primary_TCGA_shared_miRNA$p_value_wald_test),] %>%
  pull(var=1) %>%
  as.matrix(nrow=1)
```

Now, we will aggregate the ordered shared miRNAs 
``` {r aggregate_miRNAs}
Primary_glist <- c(Primary_AMLPMP_ordered_shared_miRs, Primary_TCGA_ordered_shared_miRs)

miRNA_agg <- aggregateRanks(glist = Primary_glist, method = "RRA", exact = T)
miRNA_agg
```

Now, we will aggregate the ordered shared miRNAs 
``` {r aggregate_miRNAs}
Primary_glist <- c(Primary_AMLPMP_ordered_shared_miRs, Primary_TCGA_ordered_shared_miRs)

miRNA_agg <- aggregateRanks(glist = Primary_glist, method = "stuart", exact = T)
miRNA_agg
```

The p-values are all at 1 - why? because this method relies on comparing relative positions between miRNAs within the data (eg. whether a>b in both datasets). The positions of the miRNAs are highly inconsistent relative to one another between these datasets so the package is unable to come up with a p-value


