---
title: "CBC_time"
author: "Patrick Lac"
date: "May 13, 2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

``` {r library, message = F}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(rstatix)
library(multcomp)
```

Let's begin by importing our data:

``` {r import.data}
metadata <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Peripheral bleeds/Data/BMT_MetaData.csv")
JL_data <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Peripheral bleeds/Data/JL_532_BMT_Data.csv")
MB_data <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Peripheral bleeds/Data/MB_532_BMT_Data.csv")
PL_data <- read.csv("F:/Git/PLac Analyses/miR-532 project/miR-532/Peripheral bleeds/Data/PL_532_BMT_Data.csv")
```

Next lets attach the different peripheral blood data together:
``` {r combine.data}
Total_PB_data <- rbind(JL_data, MB_data, PL_data)
head(Total_PB_data)
```

We will make a copy of the total data for manipulation:
``` {r data.copy}
Data.copy <- Total_PB_data
```

Next we will filter for CBC data
``` {r filter.11weeks}
Data.wk5 <- subset(Data.copy, Weeks.post.transplant == 5)

week10data <- subset(Data.copy, Weeks.post.transplant == 10)
week11data <- subset(Data.copy, Weeks.post.transplant == 11)
Data.wk11 <- rbind(week10data, week11data)
Data.wk11$Weeks.post.transplant <- 11

week16data <- subset(Data.copy, Weeks.post.transplant == 16)
week17data <- subset(Data.copy, Weeks.post.transplant == 17)
week18data <- subset(Data.copy, Weeks.post.transplant == 18)
Data.wk17 <- rbind(week16data, week17data, week18data)
Data.wk17$Weeks.post.transplant <- 17
```
Next we will bind these our data together
``` {r binddata}
Graph.data <- rbind(Data.wk5, Data.wk11, Data.wk17)
Graph.data$Weeks.post.transplant <- as.factor(Graph.data$Weeks.post.transplant)
```

Let's make a function to find the mean and standard deviation for each column
```{r mean_sd}
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}
```

Now we will summarize the data:
``` {r datasummary}
summary.WBC <- data_summary(Graph.data, varname = "WBC", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.RBC <- data_summary(Graph.data, varname = "RBC", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.HGB <- data_summary(Graph.data, varname = "HGB", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.HCT <- data_summary(Graph.data, varname = "HCT", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.MCV <- data_summary(Graph.data, varname = "MCV", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.MCH <- data_summary(Graph.data, varname = "MCH", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.MCHC <- data_summary(Graph.data, varname = "MCHC", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.PLT <- data_summary(Graph.data, varname = "PLT", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.MPV <- data_summary(Graph.data, varname = "MPV", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.RDW <- data_summary(Graph.data, varname = "RDW", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.Number.Lym <- data_summary(Graph.data, varname = "Number.Lym", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.Number.Mon <- data_summary(Graph.data, varname = "Number.Mon", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.Number.Gra <- data_summary(Graph.data, varname = "Number.Gra", groupnames = c("Treatment", "Weeks.post.transplant"))
summary.GFP <- data_summary(Graph.data, varname = "GFP", groupnames = c("Treatment", "Weeks.post.transplant"))
```

Now let's try to make a line plot:
```{r lineplot.WBC}
df <- data.frame(
  x=c("5","11","17"),
  y=c(10,10,12),
  text= c("#1","#2", "#3"))

lineplot.WBC <- ggplot(data=summary.WBC, aes(x=Weeks.post.transplant,y=WBC, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=WBC-sd, ymax=WBC+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 13) +
  labs(title = "White blood cells", x = "Weeks post-transplant", y = "WBC (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=10, label="p=0.11") +
  annotate("text", x=2, y=10, label="p=0.58") +
  annotate("text", x=3, y=12, label="p=0.94")

lineplot.WBC
```

```{r lineplot.RBC}
lineplot.RBC <- ggplot(data=summary.RBC, aes(x=Weeks.post.transplant,y=RBC, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=RBC-sd, ymax=RBC+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 16) +
  labs(title = "Red blood cells", x = "Treatment", y = "RBC (10"^"6"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=14, label="p=0.018") +
  annotate("text", x=2, y=14, label="p=0.45") +
  annotate("text", x=3, y=14, label="p=0.59")

lineplot.RBC
```
```{r lineplot.HGB}
lineplot.HGB <- ggplot(data=summary.HGB, aes(x=Weeks.post.transplant,y=HGB, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=HGB-sd, ymax=HGB+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 25) +
  labs(title = "Hemoglobin", x = "Treatment", y = "HGB (g/dL)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=18, label="p=0.1") +
  annotate("text", x=2, y=19, label="p=0.49") +
  annotate("text", x=3, y=18, label="p=0.7")
lineplot.HGB
```

```{r lineplot.HCT}
lineplot.HCT <- ggplot(data=summary.HCT, aes(x=Weeks.post.transplant,y=HCT, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=HCT-sd, ymax=HCT+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 80) +
  labs(title = "Hematocrit", x = "Treatment", y = "HCT (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=65, label="p=0.085") +
  annotate("text", x=2, y=65, label="p=0.51") +
  annotate("text", x=3, y=65, label="p=0.71")

lineplot.HCT
```

```{r lineplot.MCV}
lineplot.MCV <- ggplot(data=summary.MCV, aes(x=Weeks.post.transplant,y=MCV, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=MCV-sd, ymax=MCV+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(35, 55) +
  labs(title = "Mean corpuscular volume", x = "Treatment", y = "MCV ("~mu~"m"^"3"*")") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=49, label="p=0.19") +
  annotate("text", x=2, y=49, label="p=0.43") +
  annotate("text", x=3, y=49, label="p=0.45")

lineplot.MCV
```

```{r lineplot.MCH}
lineplot.MCH <- ggplot(data=summary.MCH, aes(x=Weeks.post.transplant,y=MCH, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=MCH-sd, ymax=MCH+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 20) +
  labs(title = "Mean corpuscular hemoglobin", x = "Treatment", y = "MCH (pg)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=17, label="p=0.29") +
  annotate("text", x=2, y=17, label="p=0.77") +
  annotate("text", x=3, y=17, label="p=0.29")

lineplot.MCH
```

```{r lineplot.MCHC}
lineplot.MCHC <- ggplot(data=summary.MCHC, aes(x=Weeks.post.transplant,y=MCHC, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=MCHC-sd, ymax=MCHC+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(10, 40) +
  labs(title = "Mean corpuscular \n hemoglobin concentration", x = "Treatment", y = "MCHC (g/dl)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=35, label="p=0.47") +
  annotate("text", x=2, y=35, label="p=0.72") +
  annotate("text", x=3, y=37, label="p=0.86")

lineplot.MCHC
```

```{r lineplot.PLT}
lineplot.PLT <- ggplot(data=summary.PLT, aes(x=Weeks.post.transplant,y=PLT, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=PLT-sd, ymax=PLT+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 1600) +
  labs(title = "Platelets", x = "Treatment", y = "PLT (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=1000, label="p=0.36") +
  annotate("text", x=2, y=1200, label="p=0.026") +
  annotate("text", x=3, y=1250, label="p=0.15")

lineplot.PLT
```

```{r lineplot.MPV}
lineplot.MPV <- ggplot(data=summary.MPV, aes(x=Weeks.post.transplant,y=MPV, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=MPV-sd, ymax=MPV+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 10) +
  labs(title = "Mean platelet volume", x = "Treatment", y = "MPV ("~mu~"m"^"3"*")") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=8, label="p=0.93") +
  annotate("text", x=2, y=8, label="p=0.2") +
  annotate("text", x=3, y=8, label="p=0.93")

lineplot.MPV
```

```{r lineplot.RDW}
lineplot.RDW <- ggplot(data=summary.RDW, aes(x=Weeks.post.transplant,y=RDW, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=RDW-sd, ymax=RDW+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(5, 30) +
  labs(title = "RBC distribution width", x = "Treatment", y = "RDW (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=20, label="p=0.67") +
  annotate("text", x=2, y=20, label="p=0.59") +
  annotate("text", x=3, y=20, label="p=0.28")

lineplot.RDW
```
```{r lineplot.Number.Lym}
lineplot.Number.Lym <- ggplot(data=summary.Number.Lym, aes(x=Weeks.post.transplant,y=Number.Lym, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=Number.Lym-sd, ymax=Number.Lym+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
   ylim(0, 8) +
  labs(title = "Lymphocyte count", x = "Treatment", y = "Lym (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=4.5, label="p=0.47") +
  annotate("text", x=2, y=6, label="p=0.8") +
  annotate("text", x=3, y=6, label="p=0.68")

lineplot.Number.Lym
```

```{r lineplot.Number.Mon}
lineplot.Number.Mon <- ggplot(data=summary.Number.Mon, aes(x=Weeks.post.transplant,y=Number.Mon, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=Number.Mon-sd, ymax=Number.Mon+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 1.25) +
  labs(title = "Monocyte count", x = "Treatment", y = "Mon (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=0.75, label="p=0.44") +
  annotate("text", x=2, y=0.8, label="p=0.7") +
  annotate("text", x=3, y=0.85, label="p=0.96")

lineplot.Number.Mon
```

```{r lineplot.Number.Gra}
lineplot.Number.Gra <- ggplot(data=summary.Number.Gra, aes(x=Weeks.post.transplant,y=Number.Gra, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=Number.Gra-sd, ymax=Number.Gra+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(-1, 8) +
  labs(title = "Granulocyte count", x = "Treatment", y = "Gra (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=4.5, label="p=0.13") +
  annotate("text", x=2, y=4.5, label="p=0.58") +
  annotate("text", x=3, y=4.5, label="p=0.56")

lineplot.Number.Gra
```

```{r lineplot.GFP}
lineplot.GFP <- ggplot(data=summary.GFP, aes(x=Weeks.post.transplant,y=GFP, group=Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=GFP-sd, ymax=GFP+sd), width=.1, size = 1, position=position_dodge(0.05)) +
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 105) +
  labs(title = "PB Engraftment", x = "Treatment", y = "GFP+ (%)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14)) +
  annotate("text", x=1, y=10, label="p=") +
  annotate("text", x=2, y=10, label="p=") +
  annotate("text", x=3, y=10, label="p=")

lineplot.GFP
```

### Now let's arrange the plots:
#### Figure 1
```{r fig1, fig.width=10, fig.height=11}
fig1 <- ggarrange(lineplot.WBC, lineplot.RBC, lineplot.PLT, lineplot.Number.Lym, lineplot.Number.Mon, lineplot.Number.Gra,
          labels = "auto",
          ncol=3, nrow=2, common.legend = T, legend="bottom")
fig1
```     

#### Figure 2
```{r fig2, fig.width=10, fig.height=11}
fig2 <- ggarrange(lineplot.HCT, lineplot.MPV, lineplot.HGB, lineplot.RDW, lineplot.MCV, lineplot.MCH, lineplot.MCHC, lineplot.GFP,
         labels = "auto",
          ncol=3, nrow=3, common.legend = T, legend="bottom")
fig2
```   

Now let's try to make a line plot:
```{r lineplot.WBC}
lineplot.WBC.all <- ggplot(data=Graph.data, aes(x=Weeks.post.transplant,y=WBC, group=Treatment, color=Treatment)) +
  
  geom_line(size=1.25)+
  geom_point(size=2) +
  ylim(0, 13) +
  labs(title = "White blood cells", x = "Weeks post-transplant", y = "WBC (10"^"3"*"/"~mu~"L)") +
  theme(plot.title = element_text(hjust=0.5), text=element_text(size=14)) +
  theme(axis.text = element_text(size=12), axis.title = element_text(size=14))

lineplot.WBC.all
```